\documentclass[a4paper]{article}

\usepackage{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{amssymb}
\usepackage{mathptmx}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

\titleformat{\section}{\Large\scshape}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries\large}{\hspace{-1.2em}$\blacktriangleright$}{.5em}{}[]
\titleformat{\subsubsection}[runin]{\itshape}{$\triangledown$}{0.2em}{}[]

\titlespacing{\section}{0em}{1em}{1em}
\renewcommand{\maketitle}
{
	\begin{center}
		{\huge\bfseries
		\theauthor}
	
		\vspace{.2cm}
		\href{mailto:petermanyara@outlook.com}{\ttfamily\color{blue!80!black!90}petermanyara@outlook.com}
	\end{center}
	
}
%\titleformat{command}[shape]{format}{label}{sep}{before-code}[after-code]
\geometry{margin=1in}

%opening
\title{R\'esum\'e}
\author{Peter Manyara}

\begin{document}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%
%% B I O   D A T A %%%
%%%%%%%%%%%%%%%%%%%%%%
\section{Bio Data}
\subsubsection{Date of Birth}
2nd July 1996
\subsubsection{Gender}
Male
\subsubsection{Nationality}
Kenyan
\subsubsection{Languages}
English and Kiswahili (Written and spoken)

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% O B J E C T I V E S %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Objectives}
\begin{itemize}
	\item To engage with professionals in science and engineering to gain skill and experience.
	\item To apply skills gained in improvement of production.
	\item To come up with solutions that can make a difference in the world. 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% S K I L L S   A N D   I N T E R E S T S %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills and Interests}
\subsection{Electronics Skills}
\subsubsection{General}
Electronics troubleshooting, electrical machine installation and maintenance.
\subsubsection{Embedded Systems}
I have a working knowledge of Raspberry Pi, ESP32 and Arduino prototyping boards.

\subsection{Computer Skills}
\subsubsection{Microsoft Windows}
Extensive experience in all GUI aspects. Basic proficiency with the command prompt. Better powershell proficiency.
\subsubsection{Linux}
Formidable working precision with the terminal.
\subsubsection{Microsoft Office}
Highly skilled.

\subsection{Programming}
\subsubsection{Programming Languages}
Python3, Octave, MATLAB, C++, Intel Assembly, C
\subsubsection{Markup}
\LaTeX, Markdown, HTML
\subsubsection{Graphics}
Inkscape, AutoCAD, GIMP
\subsubsection{Hardware}
Network configuration

\subsection{Workshop Skills}
\subsubsection{Metal Working}
Arc Welding, Gas Welding, TIG Welding, Use of hand and machine tools.
\subsubsection{Electricals}
Installation (wall and overhead fixtures), Electrical machines: Transformers and Motors.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% E X P E R I E N C E S %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\subsection{Engineering Intern --- Electromag Engineering Ltd}
August 2019 --- October 2019 (Fourth Year Industrial attachment)
\subsubsection{Learning areas}
Experience was gained in the following areas:
\begin{itemize}
	\item Workplace safety.
	\item Cable laying and termination.
	\item Automation of Lube blending and filling machines.
	\item Installation of industrial sockets and HI-bay factory lighting.
	\item Cable tray and cable trunk mounting.
	\item Distribution board and consumer control unit termination.
\end{itemize}
\subsubsection{Highlights}
Improvised a draw-wire technique that reduced time and effort required in laying long stretches of armored cabling.

Recommended a simplified wiring scheme to OEM\footnote{OCME Engineering} commissioning engineer to avoid working at height while integrating a non-OEM filling valve for OCME filling machine. Recommendation was adopted by the commissioning engineer.

\subsection{Engineering Intern --- KPLC Lanet}
July 2018 --- October 2018 (Third Year Industrial attachment)
\subsubsection{Learning areas}
I gained experience by observing and participating in the following activities:
\begin{itemize}
	\item Grid monitoring via SCADA system.
	\item Inspection of transmission pylons.
	\item Scheduled maintenance of power transformer and on-load tap changer.
	\item Functional testing of substation protection system.
	\item Write-up of maintenance reports.
\end{itemize}
\subsubsection{Highlights}
Participated in conversion of a 36kV CG\footnote{Crompton-Greaves} breaker's control circuitry to $110V_{AC}$ from $30V_{DC}$. This involved appropriation of components from older, decommissioned breakers.

Drafted floor plans on AutoCAD for the conversion of the Lanet depot warehouse into E-Plant department's workshop.

\subsection{Engineering Intern --- New KCC Nyahururu}
July 2017 --- September 2017 (2nd Year Industrial attachment)
\subsubsection{Learning Areas}
Experienced was gain through participation in the following activities:
\begin{itemize}
	\item Scheduled service and maintenance of factory generator. Involved replacement of air, fuel and oil filters, functional test of changeover switch.
	\item Monitoring and supervised operation of milk processing equipment. This includes pasteurizer, sterilizer and homogenizer.
	\item Operation of packaging equipment. This involved replacement of the packaging reel and cleaning-in-place prior to operation or when milk product changed.
	\item Boiler maintenance. This involved de-sooting (The boiler was a fire-in-tube type.)
\end{itemize}
\subsubsection{Highlights}
Ammonia refrigeration plant maintenance. Involved constant replacement of ammonia gas cans.

Diagnosis and repair of decommissioned homogenizer to working status. An undocumented maintenance action had left the oil pump reversed. The machine wouldn't start due to anomalous oil pressure readings.

10,000th-hour service of TCA-200 packaging machine under supervision of a Tetra Pak Engineer.

\subsection{Driver --- Jamhuri Farm}
April 2015 --- September 2015
\subsubsection{Responsibilities}
\begin{itemize}
	\item Daily delivery of fresh farm produce to hotels and resale points in Nyahururu town.
	\item Maintenance and operation of farm machinery over the course of daily production.
\end{itemize}
\subsubsection{Highlights}
First professional driving experience after acquisition of driver's license.

Operation of combine harvester for 2015 wheat harvest season (CLAAS Mercator 75) under professional tutelage.

Replacement of front axle of 4WD Massey Fergusson tractor.

%%%%%%%%%%%%%%%%%%%%%%%%
%% E D U C A T I O N %%%
%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\subsection{Jomo Kenyatta University of Agriculture and Technology}
September 2015 --- November 2020
Bachelor of Science in Electrical and Electronics Engineering
\subsection{St. Anne's Catholic Institute Nyahururu}
July 2016 --- August 2016
Certificate in Computer programming
January 2015 --- June 2015
Certified Public Accountant I
\subsection{Alliance High School}
2011 --- 2014
Kenya Certificate of Secondary Education (A)
\subsection{Riverbank Academy}
Kenya Certificate of Primary Education (A)


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% P R O F E S S I O N A L   M E M B E R S H I P %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Membership in Professional Bodies}
\subsection{IEEE}
Presently a student member of the Institute of Electrical and Electronics Engineers.
\subsection{IEEE Societes}
\begin{itemize}
	\item Power and Energy Society
	\item Computer Society
	\item Industry Applications Society
	\item Special Interest Group on Humanitarian Technology.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% L E A D E R S H I P %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Leadership}
\begin{itemize}
	\item IEEE JKUAT Student Branch event organization
	\item IEEE JKUAT SIGHT founding (Presently the Executive Committee Secretary)
	\item Society of Engineering Students Projects peer training.
	\item Mentoring or primary school kids as a high scholar in a national school.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%
%% H O B B I E S %%%
%%%%%%%%%%%%%%%%%%%%
\section{Hobbies}
\subsubsection{Reading}
Sci-Fi, Biographical non-fiction, occasional technical literature.
\subsubsection{Programming}
Proficient in python3 (used for hackathons), Linux shell, C++ (currently re-learning), once used Java, C and Intel assembly for coursework.
\subsubsection{Traveling}
A very handy application of my driving skills and temperament.
\subsubsection{Cycling}
Better than walking.
\subsubsection{Gaming}
Gaming on PC kindled my love for technology.
\subsubsection{Computer graphics}
A subject of constant interest. Stems from gaming as well.

%%%%%%%%%%%%%%%%%%%%%%
%% R E F E R E E S %%%
%%%%%%%%%%%%%%%%%%%%%%
\section{Referees}
\subsection{Njeru S. Manegene}
Lecturer,\\
Department of Electrical and Electronics Engineering,\\
Jomo Kenyatta University of Agriculture and Technology,\\
P.O. Box 62000 --- 0020,\\
Nairobi\\
\href{mailto:smanegene@gmail.com}{\ttfamily\color{blue!80!black!90}smanegene@gmail.com}

\subsection{Paul Makau}
Managing Director,\\
Electromag Engineering Limited,\\
\href{mailto:pmakau@electromag.co.ke}{\ttfamily\color{blue!80!black!90}pmakau@electromag.co.ke}

\subsection{Bisky I. Asyago}
Electrical Plant Engineer,\\
Kenya Power and Lighting Co. Ltd.,\\
\href{mailto:BAsyago@kplc.co.ke}{\ttfamily\color{blue!80!black!90}BAsyago@kplc.co.ke}

\subsection{Bernard Njoroge}
Factory Engineer,\\
New K.C.C. Limited,\\
\href{mailto:info@newkcc.co.ke}{\ttfamily\color{blue!80!black!90}info@newkcc.co.ke}

\end{document}
