\documentclass[10pt]{article}

\usepackage{lmodern}
\usepackage[default]{cantarell}
\usepackage{xcolor}
\usepackage[margin=0in]{geometry}
\usepackage{fontawesome}
\usepackage{tcolorbox}
\usepackage{marvosym}
\usepackage[hidelinks]{hyperref}

\input{cvMacros.tex}

\begin{document}
% - - - - - - - - - - - - - - - - - - - -
% P r e a m b l e
%
\begin{center}
\begin{minipage}{0.92\textwidth}
	\raggedright
		\myName{Peter Manyara}
		\myOccupation{Electrical and Electronics Engineering Student}
		% Summary
		\normalsize{A fifth year student pursuing Electrical and Electronics Engineering with skills and an understanding of how to apply engineering knowledge. An enthusiastic and motivated individual who is committed to a career in the engineering field.}
\end{minipage}
\end{center}

\myContacts{
	\myEmail{petermanyara@outlook.com}
	\myPhone{+254702672578} 
	\myGithub{github.com/liquidstar}
	\myLinkedin{linkedin.com/in/peter-manyara}
}

% - - - - - - - - - - - - - - - - - - - -
\begin{center}
	% - - - - - - - - - - - - - - - - - - - -
	% Left Column
	%
	\begin{minipage}[t]{0.45\textwidth}
		\vspace{0.2cm}
		\raggedright
		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{EDUCATION}
		% = = = = = = = = = =
		\cvBoldSubsection{Study Program}{Jomo Kenyatta University of Agriculture and Technology}{08/2015 - Present}
		\bulletpoint{B.Sc. Electrical and Electronics Engineering}
		\descr{Expected graduation 12/2020}
		\vspace{0.3cm}

		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{WORK EXPERIENCE}
		% = = = = = = = = = =
		\cvBoldSubsection{Engineering Intern}{Electromag Engineering Ltd.}{08/2019 -- 11/2019}
		\cvSubsection{Achievements/Tasks}
			\bulletpoint{TOTAL\textregistered\ Occupational Health and Safety induction training.}
			\bulletpoint{Pakscan\textregistered\ pump and valve controller network.}
			\bulletpoint{Wiring of power and control infrastructure for OCME\textregistered\ filling machines.}
			\bulletpoint{AC motor starters. e.g. DOL, $Y$ -- $\Delta$.}
			\bulletpoint{High voltage protection devices e.g. VCB, OCB, ACB and SF6 breakers.}
		\vspace{0.3cm}

		% = = = = = = = = = =
		\cvBoldSubsection{E--Plant and Protection Intern}{Kenya Power and Lighting Co.}{07/2018 - 10/2018}
		\cvSubsection{Achievements/Tasks}
			\bulletpoint{Scheduled maintenance of power transformers in substations within the Central Rift region. Up to 10~MVA.}
			\bulletpoint{Functional testing of substation protection systems e.g. Instrumentation transformers \& relays.}
			\bulletpoint{Design and development of Lanet E--Plant (Electrical Plant) reclamation project using AutoCAD\textregistered\ diagramming.}
			\bulletpoint{Ability to author concise maintenance and action reports for efficient archiving or candid escalation of technical issues.}
			\bulletpoint{Working with regional control to facilitate safe switching and thus minimize system downtime during maintenance.}
			\vspace{0.3cm}

		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{CERTIFICATES}
			\cvSubsection{Visual Basic .NET}
			%\cvSubsection{Microsoft Cerfification: Azure Fundamentals}
			\cvSubsection{International Computer Driving License}
	\end{minipage}
	\hspace{5pt}
	% - - - - - - - - - - - - - - - - - - - -
	% Right Column
	%
	\begin{minipage}[t]{0.45\textwidth}
		\vspace{0.2cm}
		\raggedright
		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{SKILLS}
			\skill{Python}
			\skill{Perl}
			\skill{Regex}
			\skill{Bash}
			\skill{Arduino}
			\skill{C++}
			\skill{C}
			\skill{x86 Assembly}
			\skill{Multisim}
			\skill{\LaTeX}
			\skill{\faGit}
			\skill{Embedded Systems}
			\skill{Matlab}
			\skill{AutoCAD}
			\vspace{0.5cm}

		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{PERSONAL PROJECTS}
		% = = = = = = = = = =
		\cvSubsection{Final Year Project}
			\bulletpoint{Simulation of BER for OFDM variant in a fading channel. MATLAB}
		% = = = = = = = = = =
		\cvSubsection{Internet Connected LED Billboard using Raspberry Pi}
			\bulletpoint{LED billboard controller using hzeller/rpi-rgb-led-matrix library and remote login via SSH. Bash, Python, C, git}
		% = = = = = = = = = =
		\cvSubsection{Elevator controller based on Intel 8086 $\mu$P}
			\bulletpoint{A motor actuator that determines the carriage position by prodigious use of limit switches. x86 Assembly, Bash.}
		\cvSubsection{IoT actuator using ESP32}
			\bulletpoint{An internet connected controller for an irrigation valve actuator. Arduino, C}
			\vspace{0.5cm}

		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{ACTIVITIES}
		% = = = = = = = = = =
		\cvSubsection{SIGHT IEEE Jomo Kenyatta University Student Branch -- Secretary (08/2019 - 08/2020)}
		\descr{Planning activities while ensuring nominal functioning of the interest group while bridging the students branch with Kenya Section.}
		% = = = = = = = = = =
		\cvSubsection{Society of Engineering Students -- Projects Chair (04/2018 - 04/2019)}
		\descr{Coordinating the society's showcase project teams while providing training for new members in embedded electronics and programming.}
		\vspace{0.5cm}
		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{INTERESTS}
			\interest{DevOps}
			\interest{GNU/Linux}
			\interest{Hardware}
			\interest{CAD}
			\interest{Mentorship}
			\interest{Humanitarian Activities}
			\interest{Financial Services}
			\interest{Renewable Energy}
			\interest{Telecommunication}
	\end{minipage}
\end{center}
\end{document}
