\documentclass[10pt]{article}

\usepackage{lmodern}
\usepackage[default]{cantarell}
\usepackage{xcolor}
\usepackage[margin=0in]{geometry}
\usepackage{fontawesome}
\usepackage{tcolorbox}
\usepackage{marvosym}

\input{cvMacros.tex}

\begin{document}
% - - - - - - - - - - - - - - - - - - - -
% P r e a m b l e
%
\begin{center}
\begin{minipage}{0.92\textwidth}
	\raggedright
		\myName{Rosemary Litunya}
		\myOccupation{Electrical and Electronics Engineering Student}
		% Summary
		\normalsize{A fifth year student pursuing Electrical and Electronics Engineering with skills and an understanding of how to apply {engineering} knowledge. An enthusiastic and motivated individual who is committed to a career in the engineering field.}
\end{minipage}
\end{center}

\myContacts{
	\myEmail{litunyar16@gmail.com}
	\myPhone{+254700470103} 
	\myLocation{Nairobi, Kenya} 
	\myLinkedin{linkedin.com/in/rosemary-litunya}
	%\myGithub{github.com/}
}

% - - - - - - - - - - - - - - - - - - - -
\begin{center}
	% - - - - - - - - - - - - - - - - - - - -
	% Left Column
	%
	\begin{minipage}[t]{0.45\textwidth}
		\vspace{0.2cm}
		\raggedright
		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{EDUCATION}
		% = = = = = = = = = =
		\cvBoldSubsection{Study Program}{Jomo Kenyatta University of Agriculture and Technology}{08/2015 - Present}
		\bulletpoint{B.Sc. Electrical and Electronics Engineering}
		\descr{Expected graduation 11/2020}
		\vspace{0.3cm}

		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{WORK EXPERIENCE}
		% = = = = = = = = = =
		\cvBoldSubsection{Electrical Intern}{Standard Rolling Mills}{08/2019 -- 11/2019}
		\cvSubsection{Achievements/Tasks}
			\bulletpoint{DC motors weekly maintenance}
			\bulletpoint{General maintenance of 4Hi transformers}
			\bulletpoint{Installation and service of 3$\mathbf\varphi$ motors up to 90~kW.}
			\bulletpoint{AC motor starters. e.g. DOL, $Y$ -- $\Delta$, Dahlander.}
			\bulletpoint{High voltage protection devices e.g. VCB, OCB, ACB and SF6 breakers.}
			\bulletpoint{Industrial power factor correction using different capacitors.}
			\bulletpoint{Maintenance on high bay cranes up to 20 tonnes load capacity.}
		\vspace{0.3cm}

		% = = = = = = = = = =
		\cvBoldSubsection{Solutions Architect Intern}{Safaricom PLC}{07/2018 - 10/2018}
		\cvSubsection{Achievements/Tasks}
			\bulletpoint{Supporting the enterprise sales process by liaising with the Enterprise Account managers to understand customer requirements and working environment and providing required technical input during sales initiatives.}
			\bulletpoint{Design and development of solutions that meet customer requirements by use of diagramming tools like Microsoft Visio.}
			\bulletpoint{Ability to clearly explain to customers Safaricom solutions in view of their requirements and in comparison to other competitive solutions.}
			\bulletpoint{Working with other teams to streamline internal processes and thus improve service delivery.}
			\vspace{0.3cm}

		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{CERTIFICATES}
			\cvSubsection{Visual Basic .NET}
			\cvSubsection{Microsoft Cerfification: Azure Fundamentals}
			\cvSubsection{International Computer Driving License}
	\end{minipage}
	\hspace{5pt}
	% - - - - - - - - - - - - - - - - - - - -
	% Right Column
	%
	\begin{minipage}[t]{0.45\textwidth}
		\vspace{0.2cm}
		\raggedright
		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{SKILLS}
			\skill{Python}
			\skill{Internet Solutions Design}
			\skill{Android Studio}
			\skill{Arduino}
			\skill{C++}
			\skill{C}
			\skill{Multisim}
			\skill{\LaTeX}
			\skill{\faGit}
			\skill{Embedded Systems}
			\skill{Matlab}
			\vspace{0.5cm}

		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{PERSONAL PROJECTS}
		% = = = = = = = = = =
		\cvSubsection{Final Year Project}
			\bulletpoint{Simulation of BER for OFDM variant in a fading channel. MATLAB}
		% = = = = = = = = = =
		\cvSubsection{Mwangaza Systems}
			\bulletpoint{Solar powered remotely controlled valve actuator for industry application. Arduino, C++, Eagle.}
		% = = = = = = = = = =
		\cvSubsection{Techtalk}
			\bulletpoint{Android application aimed at teaching sign language with different proficiency levels. Java, XML.}
			\vspace{0.5cm}

		%_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-_-
		\cvSection{ACTIVITIES}
		% = = = = = = = = = =
		\cvSubsection{IEEE Jomo Kenyatta University Student Branch -- Chair (04/2019 - Present)}
		\descr{Coordinate activities while ensuring normal running of students club while bridging the students branch with Kenya Section}
		% = = = = = = = = = =
		\cvSubsection{Tech Expo -- Projects Manager (03/2019 - 03/2020)}
		\descr{Assemble and coordinate students projects while managing project resource allocations and timelines.}
		% = = = = = = = = = =
		\cvSubsection{Society of Engineering Students -- Mentorship Chair (02/2019 - 02/2020)}
		\descr{Provide capacity building opportunities to members and provide a bridge between the industry and students.}
		% = = = = = = = = = =
		\cvSubsection{Technovation -- Coach (03/2018 - 06/2019)}
		\descr{Taught high school girls basic programming principles around OOP and assisted them in developing android applications using Java and XML.}
		\vspace{0.5cm}
		% = = = = = = = = = =
		\cvSection{INTERESTS}
			\interest{Telecommunication}
			\interest{Software}
			\interest{Hardware}
			\interest{Photonics}
			\interest{Mentorship}
			\interest{Humanitarian Activities}
			\interest{Financial Services}
	\end{minipage}
\end{center}
\end{document}
